Postural developments mediate children's visual access to social information

### 2018-01-29 writeup-cogsci/cogsci2018_faceOnly_alessandro.Rmd
smoothing edits

abstract: 
  "The ability to process social cues--including eye gaze--is a critical component of children's early language and cognitive development. However, as children reach their first birthday, they begin to locomote themselves, walking and exploring their visual environment in an entirely new way. How do these postural and locomotive changes affect children's access to the social information relevant for word-learning? Here, we explore this question by using head-mounted cameras to record infants' (8-16 months of age) egocentric visual perspective and use computer vision algorithms to detect the proportion of faces and hands in infants' environments. We find that infants' posture and orientation to their caregiver largely mediate infants' access to socially informative features, suggesting that postural and locomotive developments play a significant role in the emergence of children's linguistic and social capacities. Broadly, we suggest that the combined use of head-mounted cameras and the application of new computer vision techniques is a promising avenue for understanding the statistics of infants' visual and linguistic experience."

@@

Children are deeply engaged in learning from others [@csibra2009natural; @meltzoff2007like] and attend to the social information in their environment from their earliest days. Even newborns tend to prefer to look at faces with direct vs. averted gaze [@farroni2002eye] and follow overt gaze shifts by 6 months of age [@gredeback2008microstructure; @gredeback2010development]. And when infants free-view videos, they tend to look mostly at faces at the expense of other visual information--though older infants start to look towards people's hands and the actions they are performing [@frank2012measuring; @frank2014visual].

However, as children are learning from others around them, their view of the world is also changing radically [@adolph2007]. Infants' motor abilities improve dramatically near the end of the first year of life, allowing them to locomote independently. These motor changes have drastic consequences for what children see; crawling and walking infants have radically different views of the world. For example, during spontaneous play in a laboratory playroom, toddlers are more likely to look at the floor while crawling than while walking [@franchak2011]; in general, walking infants tend to have full visual access to their environment and the people in it, while crawling infants do not [@kretch2014].

One possibility is that these motor improvements have strong developmental cascades, impacting children’s emerging social, cognitive, and linguistic abilities [@iverson2010]. Indeed, these postural changes also impact how children interact with their mothers; walking (vs. crawling) infants make different kinds of object-related bids for attention from their mothers and tend to hear more action directed statements (e.g., “open it”) [@karasik2014]. Further, in an observational study, @walle2014 found that children who were able to walk had both higher receptive and productive vocabularies. On their account, children’s ability to stand and independently locomote may fundamentally change their ability to access social information (e.g., faces, gaze) relative to children who are still crawling and sitting. In other words, the ability to walk and move around independently and subsequently access more detailed social information may accelerate infants’ ability to learn from the people in their environments.

Recent technological developments allow for testing of this hypothesis by documenting the experiences of infants and children from their own perspective. By using head-mounted cameras, researchers have begun to document visual experiences of infants and children — which even for walking children are radically different from the adult perspective (and not easily predicted by our own adult intuitions) [@clerkin2017;@franchak2011;@yoshida2008]. Children’s views tend to be restricted and to be dominated by objects and hands much more than that of adults [@yoshida2008], and both computational and empirical work suggest that this restricted viewpoint may be more effective for learning objects and their labels than the comparable adult perspective [@bambach2017;@yurovsky2012]. Further, recent work also suggests dramatic changes in the child’s perspective over the first two years of life, as views transition from primarily containing a close up view of faces to capturing views of hands paired with the objects they are acting on [@fausey2016].

Here, we directly ask whether postural and locomotive developments change the availability of social information--the presence of faces and hands. To do so, we recorded the visual experience of a group of infants in three age ranges (8,12, and 16 months) using head-mounted cameras during a brief laboratory free-play session; children’s posture and orientation relative to their caregiver were also recorded from a third-person perspective and hand-annotated. We then capitalize on recent improvements in face and pose detection algorithms [@zhang2016; @cao2017realtime] to analyze the frequencies of faces and hands (using wrists as a proxy for the latter) in the child’s visual environment, both overall and relative to naming events by their caregivers. We hypothesized that there would be differential access to social information based on children's postural developments: crawling infants would see fewer faces because they would primarily be looking at the ground, while walking toddlers would have access to a richer visual landscape thus enabling a larger portion of the social information in their environment to be accessible.

that would contain a larger portion of the social information in the environment.

@@

Even with the fish-eye lens, the vertical field of view of the camera is still considerably reduced compared to the child's approximate vertical field of view, which spans around 100--120$^{\circ}$ in the vertical dimension by 6-7 months of age [@mayer1988;@cummings1988]. As we were primarily interested in the presence of faces in the child's field of view, we chose to orient the camera upwards to capture the entirety of the child's upper visual field where the child is likely to see the faces of adults around them. This choice allowed us to maximize our chances of capturing faces that the child would have seen during the play session.

## Procedure

First, all parents signed consent documents in a waiting room where children were fitted with the headcam. After the child was comfortable in the waiting room and with the experimenter, the experimenter placed the headcam on the child's head. If the child was uninterested in wearing the headcam or tried to take it off, the experimenter presented engaging toys to try to draw the child's focus away from the headcam [@yoshida2008].

After the child was comfortable wearing the headcam, the child and caregiver were shown to a playroom for the free-play session--the focus of the current study. Parents were shown a box containing three pairs of novel and familiar objects (e.g., a ball and a microfiber duster, named a "zem"), and were instructed to play with the object pairs with their child one at a time, "as they typically would." All parents confirmed that their child had not previously seen the novel toys and were instructed to use the novel labels to refer to the novel toys.

The experimenter then left the playroom for approximately 15 minutes, during which a tripod-mounted camera in the corner of the room recorded the session and the headcam captured video from the child's perspective.

@@

## Face and Hand Detection
We used three face detection systems to explore infants' changing access to social information and to avoid the cost of hand-annotating every frame. The first of these is the most commonly-used and widely available face detection algorithm: Viola-Jones. We used this as a benchmark for performance; while it can achieve impressive accuracy in some situations, it is notoriously bad at dealing with occluded faces [@scheirer2014perceptual]. We next capitalized on recent improvements in computer vision, testing the performance of two face detectors that both made use of Convolutional Neural Networks (CNNs) to extract face information. The first algorithm was specifically optimized for face detection, and the second algorithm was optimized to extract information about the position of 18 different body parts belonging to an agent.

This second of the CNN-based algorithms--the pose detector--provided us with the location of an agent's wrists, which we used as a proxy for the presence of a hand. We did so first because we did not capture the entire visual field experienced by the infants/children. Thus, even though the video may only show the presence of a wrist, the caregiver's hand may be within the child's field of view. Second, we did so because hands are often occluded by objects when caregivers are interacting with children, yet still visually accessible by the child and part of their joint interaction. For example, if a caregiver was holding a toy and presenting it to the infant, their wrists may be visible but their hand may not necessarily be (as it is occluded by the toy). Similarly, we used an agent's nose (one of the 18 body parts detected) to operationalize face presence, as any half of a face necessarily contains a nose.

### Algorithms
The first face detection system made use of a series of Haar feature-based cascade classifiers [@viola2004robust] applied to each individual frame. This detector provided information about the presence of a face as well as its size and position.

The second algorithm was based on the work by @zhang2016 using multi-task cascaded convolutional neural networks (MTCNNs). The system was built using a novel cascaded CNN-based framework for joint detection and alignment, built to perform well in real-world environments where varying illuminations and occlusions are present. We used a Tensorflow implementation of this algorithm provided by (https://github.com/davidsandberg/facenet). Like Viola-Jones, this detector provided information about the presence of a face as well as its size and position.

The third algorithm was a CNN-based pose detector that provided the locations of 18 body parts (ears, nose, wrists, etc.) called OpenPose [@cao2017realtime; @simon2017hand; @wei2016cpm] avaliable at https://github.com/CMU-Perceptual-Computing-Lab/openpose. The system uses a CNN for initial anatomical detection and subsequently applies part affinity fields (PAFs) for part association, producing a series of body part candidates. The candidates are then matched to a single individual and finally assembled into a pose. For the purposes of our investigation we only made use of the body parts relevant to the face and hands (nose and wrists). We operationalized face detections as any frames containing a nose, and hand detections as any frames containing either the left or the right wrist.

### Detector evaluation
To evaluate face detector performance, we needed to construct an unbiased "gold set" of labeled frames that made sure to account for the relatively rare appearance of faces in the dataset. We thus hand-labeled two samples: a sample containing a high density of faces (half reported by MTCNN, half by OpenPose) and a random sample from the remaining frames. Each sample was comprised of an equal number of frames taken from each participant (i.e., video). Faces were classifed as present in a frame if at least half of the face was showing. Precision (hits / hits + false alarms), recall (hits / hits + misses), and F-score (harmonic mean of precision and recall) were calculated for all detectors and are reported in Table 2. For wrist detections, the "gold set" was constructed in the same manner, with the exception that frames with a high density of wrists were taken by pose detections made by OpenPose.

@@

For face detection, MTCNN outperformed OpenPose when taking into account only the composite F-score (`r round(perfFacesOverall$f[1],2)` MTCNN vs. `r round(perfFacesOverall$f[2],2)` OpenPose); thus the face presence analyses to follow all result from MTCNN detections. We found that although MTCNN and OpenPose perform comparably with the random sample, MTCNN performed better on the high density sample (specifically looking at precision), suggesting that OpenPose generated more false positives than MTCNN. ViolaJones performed quite poorly relative to the other detectors especially with respect to the random sample.

@@

# Results
First, we report developmental shifts in infants' posture and their orientation relative to their caregiver. Then, we explore how these changes influence children's visual access to faces and hands across this developmental time range. Finally, we explore how these changes impact the accessibility of faces and hands during labeling events.

@@

ggplot(detectionsByAge, aes(x = age.at.test, y = detections, color = detectorType, size=len.min)) +
    geom_jitter(width = .25) +
    geom_smooth(size=1) +
    scale_x_continuous(breaks=c(8,12,16)) +
    scale_size_continuous(range=c(.01,2),name = "Video Length (mins)") +
    labs(y = "Prop. detected", x = element_blank()) +
    theme_few() + 
    theme(legend.position="none") +
    facet_grid(~detectorType) 
```

However, we found that any age related effects were much smaller compared to the impact of postural and locomotive changes on children's visual access to faces. Children's posture was a major factor both in how many faces they saw during the play session.  Infants who were sitting saw more faces than infants who were lying down or being carried, while infants who were standing saw the most faces. We also examined how the child's orientation relative to their caregiver impacted their visual access to faces: children who were far away from their caregiver were more likely to see faces than children who were close to their caregiver; this was true within all age groups and for both face detectors.

```{r detByPosOrient, fig.env="figure*", fig.pos = "h", fig.align = "center", fig.width=7, fig.height=4, fig.cap = "Proportion face detections as a function of children's posture (top panel) and orientation (bottom panel), binned by the age of the participant."}

@@

@@

To formalize these observations, we fit a generalized linear model to the proportion of faces infants saw in each posture and orientation (as detected by MTCNN), with participant's age, orientation, and posture as independent variables. A summary of the coefficients of a model with only main effects (and no interactions) model can be found in Table 3.  When we did include interaction terms between age, posture, and orientation, age no longer remained a significant predictor (b = `r round(faceGLMOut$coef[2,1],2)`, SE = `r round(faceGLMOut$coef[2,2],2)`, z = `r round(faceGLMOut$coef[2,3],2)` , p = `r round(faceGLMOut$coef[2,4],2)`).  We found the same pattern of results for the OpenPose face detections, omitted here for brevity. We also found the same pattern with respect to infant's visual access to hands (see Table 4); including interaction terms also eliminated any main effect of age on the proportion of hands detected (b = `r round(wristGLMOut$coef[2,1],2)`, SE = `r round(wristGLMOut$coef[2,2],2)`, z = `r round(wristGLMOut$coef[2,3],2)`, p = `r round(wristGLMOut$coef[2,4],2)`). Thus, these results suggest that infants' access to social information is heavily influenced by their postural and locomotive development.

@@

## Access to Faces and Hands During Labeling Events
Finally, we analyzed how face and wrist detections changed during object labeling events as a function of infant's posture and orientation. Specfically, we analyzed a four-second window around each labeling event (e.g., "Look at the [zem]!"); these labeling events were hand-annotated and automatically synchronized with the frame-by-frame face detections. We found that infants' posture and orientations impacted the degree to which they saw their caregiver's face and wrist during a labeling event; infants who were sitting or standing were more likely to have access to this social information. However, this did not manifest in a direct change the presence of wrists/hands before vs. after naming events (average difference in proportion of wrists detected, 8 m.o. = `r round(naming_Wrists_Summary$mean[1],3)`, 12 m.o. = `r round(naming_Wrists_Summary$mean[2],3)`, 16 m.o. = `r round(naming_Wrists_Summary$mean[3],3)`) or in proportion of faces detected  (average difference in proportion of faces detected, 8 m.o. = `r round(naming_Faces_Summary$mean[1],3)`, 12 m.o. = `r round(naming_Faces_Summary$mean[2],3)`, 16 m.o. = `r round(naming_Faces_Summary$mean[3],3)`).

# General Discussion
We used a head-mounted camera to explore how children's postural and locomotive development directly impacts their access to social information, here operationalized as the presence of the faces and wrists of their caregiver. We found that children's posture and orientation towards their caregiver changed systematically across age, and that both of these factors dramatically impacted the proportion of faces and hands that were available in the child's visual field. Thus, infants' postural and locomotive developments are mediating factors that explain some of the age-related changes in the proportion of faces and wrists/hands that are visually available to infants. Broadly, this work suggests that motoric developments mediate how infants experience their visual world and the social information in it: infants that are sitting and standing have a different view of their world, the people in it, and the actions that are being performed.

>>>>

abstract: 
  "The ability to process social cues--including eye gaze--is a critical component of children's early language and cognitive development. However, as children reach their first birthday, they begin to locomote themselves, walking and exploring their visual environment in an entirely new way. How do these postural and locomotive changes affect children's access to the social information relevant for word-learning? Here, we explore this question by using head-mounted cameras to record infants' (8-16 months of age) egocentric visual perspective and use computer vision algorithms to detect the proportion of faces and wrists in infants' environments. We find that infants' posture and orientation to their caregiver largely mediates their access to social information, suggesting that postural and locomotive developments play a significant role in the emergence of children's linguistic and social capacities. Broadly, we suggest that the combined use of head-mounted cameras and the application of new computer vision techniques is a promising avenue for understanding the statistics of infants' visual and linguistic experience."

@@

Children are deeply engaged in learning from others [@csibra2009natural; @meltzoff2007like] and attend to the social information in their environment from their earliest days. Even newborns tend to prefer to look at faces with direct vs. averted gaze [@farroni2002eye] and young infants follow overt gaze shifts  [@gredeback2008microstructure; @gredeback2010development]. Further, when infants free-view videos, they tend to look mostly at faces at the expense of other visual information--though older infants start to look towards people's hands and the actions they are performing [@frank2012measuring; @frank2014visual].

However, as children are learning from others around them, their view of the world is also radically changing  [@adolph2007]. Infants' motor abilities improve dramatically near the end of the first year of life, allowing them to locomote independently. These motor changes have significant consequences for what children see; crawling and walking infants simply have different views of the world. For example, during spontaneous play in a laboratory playroom, toddlers are more likely to look at the floor while crawling than while walking [@franchak2011]; in general, walking infants tend to have full visual access to their environment and the people in it, while crawling infants do not [@kretch2014].

One possibility is that these motor improvements have strong developmental cascades, impacting children’s emerging social, cognitive, and linguistic abilities [@iverson2010]. Indeed, these postural changes also impact how children interact with their mothers; walking (vs. crawling) infants make different kinds of object-related bids for attention from their mothers and tend to hear more action directed statements (e.g., “open it”) [@karasik2014]. Further, in an observational study, @walle2014 found that children who were able to walk had both higher receptive and productive vocabularies. On their account, children’s ability to stand and independently locomote may fundamentally change their ability to access social information (e.g., faces, gaze)  and in turn to accelerate their own learning.

Recent technological developments allow for testing of this hypothesis by documenting the experiences of infants and children from their own perspective. By using head-mounted cameras, researchers have begun to record the visual experiences of infants and children-- which even for walking children are extremely different from the adult perspective (and not easily predicted by our own adult intuitions) [@clerkin2017;@franchak2011;@yoshida2008]. While children’s views tend to be more restricted and dominated by objects and hands  [@yoshida2008], both computational and empirical work suggest that this restricted viewpoint may be more effective for learning objects and their labels than the comparable adult perspective [@bambach2017;@yurovsky2012]. Further, recent work also suggests dramatic changes in the child’s perspective over the first two years of life, as views transition from primarily containing close up views of faces to capturing views of hands paired with the objects they are acting on [@fausey2016].

Here, we directly examine whether postural and locomotive developments change the availability of social information--the presence of faces and hands. To do so, we recorded the visual experience of a group of infants in three age ranges (8,12, and 16 months) using head-mounted cameras during a brief laboratory free-play session; children’s posture and orientation relative to their caregiver were also recorded from a third-person perspective and hand-annotated. We then capitalize on recent improvements in face and pose detection algorithms [@zhang2016; @cao2017realtime] to analyze the frequencies of faces and hands (using wrists as a proxy for the latter) in the child’s visual environment, both overall and relative to naming events by their caregivers. We hypothesized that there would be differential access to social information based on children's postural developments: crawling infants would see fewer faces because they would primarily be looking at the ground, while walking toddlers would have access to a richer visual landscape, thus rendering accessible a larger portion of the social information in their environment.

@@

Even with the fish-eye lens, the vertical field of view of the camera is still considerably reduced compared to the child's approximate vertical field of view, which spans around 100--120$^{\circ}$ in the vertical dimension by 6-7 months of age [@mayer1988;@cummings1988]. As we were primarily interested in the presence of faces in the child's field of view, we chose to orient the camera upwards to capture the entirety of the child's upper visual field where the child is likely to see adult faces.

## Procedure
First, all parents signed consent documents in a waiting room where children were fitted with the headcam. After the child was comfortable in the waiting room and with the experimenter, the experimenter placed the headcam on the child's head. If the child was uninterested in wearing the headcam or tried to take it off, the experimenter presented engaging toys to try to draw the child's focus away from the headcam [@yoshida2008]. After the child was comfortable wearing the headcam, the child and caregiver were shown to a playroom for the free-play session. Parents were shown a box containing three pairs of novel and familiar objects (e.g., a ball and a microfiber duster, named a "zem"), and were instructed to play with the object pairs with their child one at a time, "as they typically would." All parents confirmed that their child had not previously seen the novel toys and were instructed to use the novel labels to refer to the novel toys. The experimenter then left the playroom for approximately 15 minutes, during which a tripod-mounted camera in the corner of the room recorded the session and the headcam captured video from the child's perspective.

@@

## Face and Hand Detection
We used three face detection systems to measure infants' changing access to faces. The first of these is the most commonly-used and widely available face detection algorithm: Viola-Jones. We used this as a benchmark for performance, as while it can achieve impressive accuracy in some situations, it is notoriously bad at dealing with occluded faces [@scheirer2014perceptual]. We next capitalized tested the performance of two face detectors that both made use of recently developed Convolutional Neural Networks (CNNs) to extract face information. The first algorithm was specifically optimized for face detection, and the second algorithm was this to extract information about the position of 18 different body parts. For the second algorithm (called OpenPose) [@cao2017realtime], we used the agent's nose (one of the 18 body parts detected) to operationalize the presence of faces, as any half of a face necessarily contains a nose.

The OpenPose detector also provided us with the location of an agent's wrists, which we used as a proxy for the presence of a hand. We did so first because we did not capture the entire visual field experienced by the infants/children. Thus, even though the video may only show the presence of a wrist, the caregiver's hand may be within the child's field of view. Second, we did so because hands are often occluded by objects when caregivers are interacting with children, yet still visually accessible by the child and part of their joint interaction. For example, if a caregiver was holding a toy and presenting it to the infant, their wrists may be visible but their hand may not necessarily be (as it is occluded by the toy).

### Algorithms
The first face detection system made use of a series of Haar feature-based cascade classifiers [@viola2004robust] applied to each individual frame. This detector provided information about the presence of a face as well as its size and position.  The second algorithm (based on  work by @zhang2016) using multi-task cascaded convolutional neural networks (MTCNNs). The system was built using a novel cascaded CNN-based framework for joint detection and alignment, built to perform well in real-world environments where varying illuminations and occlusions are present. We used a Tensorflow implementation of this algorithm provided by (https://github.com/davidsandberg/facenet). Like Viola-Jones, this detector provided information about the presence of a face as well as its size and position.

The CNN-based pose detector (OpenPose [@cao2017realtime; @simon2017hand; @wei2016cpm]) provided the locations of 18 body parts (ears, nose, wrists, etc.)  avaliable at https://github.com/CMU-Perceptual-Computing-Lab/openpose. The system uses a CNN for initial anatomical detection and subsequently applies part affinity fields (PAFs) for part association, producing a series of body part candidates. The candidates are then matched to a single individual and finally assembled into a pose; here, we only made use of the body parts relevant to the face and hands (nose and wrists). We operationalized face detections as any frames containing a nose, and hand detections as any frames containing either the left orright wrist.

### Detector evaluation
To evaluate face detector performance, we constructed an unbiased "gold set" of labeled frames that accounted for the relatively rare appearance of faces in the dataset. We thus hand-labeled two samples: a sample containing a high density of faces (half reported by MTCNN, half by OpenPose) and a random sample from the remaining frames. Each sample was comprised of an equal number of frames taken from each child's video. Faces were classifed as present in a frame if at least half of the face was showing. Precision (hits / hits + false alarms), recall (hits / hits + misses), and F-score (harmonic mean of precision and recall) were calculated for all detectors and are reported in Table 2. For wrist detections, the "gold set" was constructed in the same manner, with the exception that frames with a high density of wrists were taken by pose detections made by OpenPose.

@@

For face detection, MTCNN outperformed OpenPose when taking into account only the composite F-score (`r round(perfFacesOverall$f[1],2)` MTCNN vs. `r round(perfFacesOverall$f[2],2)` OpenPose); we thus use MTCNN detections in the following analyses. Although MTCNN and OpenPose performed comparably with the random sample, MTCNN performed better on the high density sample (specifically looking at precision), suggesting that OpenPose generated more false positives than MTCNN. ViolaJones performed quite poorly relative to the other detectors, especially with respect to the random sample.

@@

# Results
First, we report developmental shifts in infants' posture and their orientation relative to their caregiver. Then, we explore how these changes influence children's visual access to faces and wrists/hands across this developmental time range. Finally, we explore how these changes impact the accessibility of faces and wrists/hands during labeling events.

@@

ggplot(detectionsByAge, aes(x = age.at.test, y = detections, color = detectorType, size=len.min)) +
    geom_jitter(width = .25) +
    geom_smooth(size=1) +
    scale_x_continuous(breaks=c(8,12,16)) +
    scale_size_continuous(range=c(.01,2),name = "Video Length (mins)") +
    labs(y = "Prop. detected", x = element_blank()) +
    theme_few() + 
    theme(legend.position="none") +
    facet_grid(~detectorType) 
```
```{r detByPosOrient, fig.env="figure*", fig.pos = "h", fig.align = "center", fig.width=7, fig.height=4, fig.cap = "Proportion face detections as a function of children's posture (top panel) and orientation (bottom panel), binned by the age of the participant."}

@@

However, we found that any age related effects were much smaller compared to the impact of postural and locomotive changes on children's visual access to faces. Children's posture was a major factor both in how many faces and wrists/hands they saw during the play session.  Infants who were sitting saw more faces than infants who were lying down or being carried, while infants who were standing saw the most faces (Figure \ref{fig:detByPosOrient}, upper panel); this same pattern was also true for wrists/hand detectinos. We also examined how the child's orientation relative to their caregiver impacted their visual access to faces and hands. Children who were far away from their caregiver were more likely to see faces than children who were close to their caregiver; this was true within all age groups  (Figure \ref{fig:detByPosOrient}, lower panel).

@@

To formalize these observations, we fit a generalized linear model to the proportion of faces infants saw in each posture and orientation (as detected by MTCNN), with participant's age, orientation, and posture as independent variables. A summary of the coefficients of a model with only main effects (and no interactions) model can be found in Table 3.  When we did include interaction terms between age, posture, and orientation, age no longer remained a significant predictor (b = `r round(faceGLMOut$coef[2,1],2)`, SE = `r round(faceGLMOut$coef[2,2],2)`, z = `r round(faceGLMOut$coef[2,3],2)` , p = `r round(faceGLMOut$coef[2,4],2)`). We also found the same pattern with respect to infant's visual access to hands (see Table 4); including interaction terms also eliminated any main effect of age on the proportion of hands detected (b = `r round(wristGLMOut$coef[2,1],2)`, SE = `r round(wristGLMOut$coef[2,2],2)`, z = `r round(wristGLMOut$coef[2,3],2)`, p = `r round(wristGLMOut$coef[2,4],2)`). Thus, these results suggest that infants' access to social information is heavily influenced by their postural and locomotive developments.

@@

## Access to Faces and Hands During Labeling Events
Finally, we analyzed how face and wrist/hand detections changed during object labeling events as a function of infant's posture and orientation. Specfically, we analyzed a four-second window around each labeling event (e.g., "Look at the [zem]!"); these labeling events were hand-annotated and automatically synchronized with the frame-by-frame face detections. We found that infants' posture and orientations impacted the degree to which they saw their caregiver's face and wrist during a labeling event; infants who were sitting or standing were more likely to have access to this social information. However, this did not manifest in a direct change the presence of wrists/hands before vs. after naming events (average difference in proportion of wrists detected, 8 m.o. = `r round(naming_Wrists_Summary$mean[1],3)`, 12 m.o. = `r round(naming_Wrists_Summary$mean[2],3)`, 16 m.o. = `r round(naming_Wrists_Summary$mean[3],3)`) or in proportion of faces detected  (average difference in proportion of faces detected, 8 m.o. = `r round(naming_Faces_Summary$mean[1],3)`, 12 m.o. = `r round(naming_Faces_Summary$mean[2],3)`, 16 m.o. = `r round(naming_Faces_Summary$mean[3],3)`).

# General Discussion
We used a head-mounted camera to explore how children's postural and locomotive development directly impacts their access to social information, here operationalized as the presence of the faces and wrists of their caregiver. We found that children's posture and orientation towards their caregiver changed systematically across age, and that both of these factors dramatically impacted the proportion of faces and wrists/hands that were available in the child's visual field. Thus, infants' postural and locomotive developments are mediating factors that explain some of the age-related changes in the proportion of faces and wrists/hands that are visually available to infants. Broadly, this work suggests that motoric developments mediate how infants experience their visual world and the social information in it: infants that are sitting and standing have a different view of their world, the people in it, and the actions that are being performed.
